Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-05 paper.tex
Cleaned up Figure 1 and added labels to improve readability
Added caption to test data generation pipeline

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}
\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\par\singlespacing\small}

@@

    \resizebox{\textwidth}{!}{
    \includegraphics{figures/archetype-memo.pdf}}

@@

\begin{lstlisting}
ink_phase = []
paper_phase = [PaperFactory(p=0.5)]
post_phase = [
  BadPhotoCopy(p=0.5),
  PencilScribbles(p=0.5),
  Markup(markup_color=(0,0,0), p=0.5)
]

AugraphyPipeline(ink_phase, paper_phase, post_phase)
\end{lstlisting}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}
\usepackage{etoolbox}
\usepackage{multirow}
\usepackage{tabularx}
\AtBeginEnvironment{quote}{\par\singlespacing\small}

@@

    \begin{tabularx}{\linewidth}{*{3}{>{\centering\arraybackslash}X}}
        Noisy Original & Clean Reproduction & Augraphy Reproduction \\
        \multicolumn{3}{c}{
            \resizebox{\textwidth}{!}{
                \includegraphics{figures/archetype-memo.pdf}}}      \\
        (a) & (b) & (c) \\
    \end{tabularx}

@@

\begin{lstlisting}[language=Python, label={lst:test-pipeline}, caption={Pipeline used for test data generation.}]
ink_phase = []
paper_phase = [PaperFactory(p=0.5)]
post_phase = [
  BadPhotoCopy(p=0.5),
  PencilScribbles(p=0.5),
  Markup(markup_color=(0,0,0), p=0.5)
]
AugraphyPipeline(ink_phase, paper_phase, post_phase)
\end{lstlisting}
